Model Checking for Open Concurrent Systems

### 2018-09-07 2018-ModelCheckingPNets/checking.tex
2 more drawings

@@

 where, $c$ is an action name expressing the communication port. $arg_{i}$ is a list of arguments, and each $arg_{i}$ is either a send expression $!e$, or a receive variable $?x$. An action $\alpha$ is a parameterised action $c(arg_{i})$ or a silent action $\tau$. $p$ is an atomic proposition and $X$ is a set of variables. $\neg$, $\vee$ and $\wedge$ are respectively negation, disjunction and conjunction operator on action formula and state formula. $[\alpha]\varphi$ expresses "whenever an action $\alpha$ happens, we will do $\varphi$", and $\langle\alpha\rangle$ expresses "an action $\alpha$ takes effective, we will do $\varphi$". $x_{i}\in X$ is a free variable bound in state formula $\varphi$. $\mu$ and $\nu$ are respectively the minimum fixed point and the maximum fixed point.\TODO{Tengfei: Must more explaination}

@@

At first, we can do $\langle start?M\rangle$ and then it enters a loop. After that, either we can do a $timeout$, and then it is done and the result is true. Or we can do a $tick$ and then we continue the loop with decrementing the value $t$ by one.

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/BIPspec-ArchFailureTimerMax-v2}
  \caption{The BIP specification of the Failure Monitor architecture}
  \label{schema:ArchFailure:BIP}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/FailureTimerOA}
  \caption{The Open Automaton of the Failure Monitor architecture}
  \label{schema:ArchFailure:OA}
\end{figure}

@@

 where, $c$ is an action name expressing the communication port. $arg_{i}$ is a list of arguments, and each $arg_{i}$ is either a send expression $!e$, or a receive variable $?x$. An action $\alpha$ is a parameterised action $c(arg_{i})$ or a silent action $\tau$. $p$ is an atomic proposition and $X$ is a set of variables. $\neg$, $\vee$ and $\wedge$ are respectively negation, disjunction and conjunction operator on action formula and state formula. $[\alpha]\varphi$ expresses "whenever an action $\alpha$ happens, we will do $\varphi$", and $\langle\alpha\rangle$ expresses "an action $\alpha$ takes effective, we will do $\varphi$". $x_{i}\in X$ is a free variable bound in state formula $\varphi$. $\mu$ and $\nu$ are respectively the minimum fixed point and the maximum fixed point.\TODO{Tengfei: Need more explanation}

@@

\ERIC{this description is too operational (like a state machine), I would like a more logical description of the formula. One way is to use the vocabulary of ``Specification patterns'', like ``it is possible'', ``it is mandatory'', ``do something until some condition'', etc}
At first, we can do $\langle start?M\rangle$ and then it enters a loop. After that, either we can do a $timeout$, and then it is done and the result is true. Or we can do a $tick$ and then we continue the loop with decrementing the value $t$ by one.
